%\begin{document} 
For this project we chose to implement two types of artificial intelligent agents for the game Bomberman.

%\subsection{A Brief Introduction}
The game Bomberman (also known as Dynablaster) is a strategic, maze-based, 2D video game franchise originally developed by Hudson Soft. It was originally published in 1983 and until now over 70 editions of this game have been released. \todo{citation needed}
The goal of the game is to complete levels by strategically placing bombs in order to eliminate enemy players and demolish obstacles. 
Bombs are the only weapon at the players disposal and are a key aspect of the game. The bombs will explode a brief amount of time after they have been placed and will kill any player that are within their reach as well as demolish up one obstacle for each one of the four directions they affect. 

Power ups are an essential part in Bomberman as it allows increases the reach of the fire of the bombs, the speed of the player and how many bombs one player can place on the map at the same time. One can image that these power ups are advantageous as it allows the player to gain more powers, speed to or from the enemy and surround enemies entirely with bombs.

To investigate the effect of power ups we have crafted two artificial intelligent agents which both employ different strategies in regards to upgrades. One AI employs a strategy to get to and kill an enemy player as fast as possible, we shall call this AI `Kill-First-AI'. The second AI first attempts to gain as much upgrades as possible before engaging the other players, we shall call this AI `Upgrade-First-AI'.
