\begin{table}
\centering
\begin{tabular}{l|l}
\textbf{AI Name} & \textbf{Number of wins}\\\hline
\textit{Kill-First-AI} & 48 \\
\textit{Upgrade-First-AI} & 27\\
\end{tabular}
\caption{Results of 100 matches between the Kill-First-AI and the
Upgrade-First-AI. The rest of the results are draws, meaning that the game did
not end within 10,000 time steps (which should equal slightly more than
2 minutes of play time if one were to play the games oneself)}
\label{tab:results}
\end{table}

In order to compare the AI's with each other, a simple benchmark tool was
created. This tool runs a number of matches and keeps the results of these
matches. After the competition is done, the number of victories per bot type is
printed. Table \ref{tab:results} shows the results of a benchmark running 100
games.

\subsection{Analysis}
When looking at the results, it can be concluded that the Kill-First-AI works
better than the Upgrade-First-AI. To find a reason for this result, we can look
at the individual games of the one versus the other.

The main cause of losing for the Upgrade-First-AI seems to be that most of the
times, the enemy has already reached it, before it is done `upgrading'. The
collecting behavior of the bot seems to work a lot worse, when the enemy is
constantly threatening him with bombs. In many situations the Upgrade-First-AI
gets himself into trouble by still placing bombs in his neighbourhood, while the
enemy tries to kill him. This results in the bot having too many bombs in its
surroundings to escape from, resulting in a lost game. 

In most games where the
Upgrade-First bot does get enough time to get all the power ups required, it beats the
opponent.


